Exploring the Composition of Lithic Assemblages in Mesolithic South-Eastern Norway

### 2022-02-08 analysis/paper/paper.Rmd
Cleaned out some unnecessary files

splt1 <- fviz_ca_col(caallcats, col.col = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE) +
  labs(colour = "Contribution to total inertia") +
  ggtitle("Supplementary material") +
  theme(legend.position = "bottom",
        plot.title = element_text(size = 23, face = "bold",
                                  family = "serif"))

>>>>

splt1 <- fviz_ca_col(caallcats, col.col = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), repel = TRUE,
             title = "A") +
  labs(colour = "Contribution to total inertia") +
  theme(legend.position = "bottom")
